---
title: "Exam 2"
format: html
---

```{r}
library(tidytuesdayR)
library(tidyverse)
library(rnaturalearth)
library(sf)

tuesdata <-tt_load("2020-02-18")
fc <- tuesdata$food_consumption
str(fc)
head(fc,22)
```

#### RQ1: Which 5 countries consume the most food are?
show the answer as a 2-column table and as a graph
sort the countries based on consumption from largest to smallest

```{r}
fc_total <- fc %>%
  group_by(country) %>%
  summarize(total_consumption = sum(consumption, na.rm = TRUE)) %>%
  arrange(desc(total_consumption)) %>%
  mutate(row = row_number())

top5 <- fc_total %>%
  filter(row <= 5) %>%
  select(-row) 

top5


library(ggplot2)
ggplot(top5, aes(x = reorder(country, total_consumption), y = total_consumption, fill = country)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Top 5 Countries by Total Food Consumption",
       x = "Country", y = "Total Consumption (kg/person/year)") +
  theme_minimal() +
  theme(legend.position = "none")

```


#### RQ2: Which top 5 countries consume each food are?
show the answer as a 3-column table(show the food category as the first column followed by country and consumption) and as a graph
for each food, sort the countries based on consumption from largest to smallest

```{r}
fc_clean <- fc %>%
  mutate(food_category = recode(food_category,
    "Milk - inc. cheese" = "Milk & Cheese",
    "Nuts inc. Peanut Butter" = "Nuts & PB",
    "Wheat and Wheat Products" = "Wheat Products",
    "Lamb & Goat" = "Lamb/Goat"
  ))

top5_food <- fc_clean %>%
  arrange(food_category, desc(consumption)) %>%
  group_by(food_category) %>%
  mutate(row = row_number()) %>%
  filter(row <= 5) %>%
  ungroup()

top5_food %>% 
  select(food_category, country, consumption)


ggplot(top5_food, aes(x = reorder(country, consumption), y = consumption, fill = food_category)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ food_category, scales = "free", ncol = 3) +
  coord_flip() +
  labs(title = "Top 5 Countries by Consumption for Each Food Category",
       x = "Country", y = "Consumption (kg/person/year)") +
  theme_minimal() +
  theme(legend.position = "none",
        strip.text = element_text(size = 10))

```

#### RQ: What does the consumption of each food look like?
```{r}
fc_clean <- fc %>%
  mutate(food_category = recode(food_category,
    "Milk - inc. cheese" = "Milk & Cheese",
    "Nuts inc. Peanut Butter" = "Nuts & PB",
    "Wheat and Wheat Products" = "Wheat Products",
    "Lamb & Goat" = "Lamb/Goat"
  ))

fc_top10 <- fc_clean %>%
  group_by(food_category) %>%
  slice_max(consumption, n = 10) %>%
  ungroup() %>%
  mutate(country = fct_reorder(country, consumption))

# Plot: Top 10 consuming countries per food
ggplot(fc_top10, aes(x = consumption, y = country)) +
  geom_col(fill = "steelblue") +
  facet_wrap(~ food_category, scales = "free_y") +
  labs(
    title = "Top 10 Countries by Food Consumption",
    subtitle = "Per food category, in kg/person/year",
    x = "Consumption (kg/person/year)",
    y = "Country"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.y = element_text(size = 7)
  )

```

