# Welcome {.unnumbered}

Welcome to my online portfolio for COMP/STAT112 course taken at [Macalester College](https://www.macalester.edu/).  Please, use the side bar on the left for navigation.

```{r}
#| output: false
#| echo: false

packages <- c("wordcloud2", "here")
```

```{r}
#| output: false
#| echo: false

install.packages(setdiff(packages, rownames(installed.packages())), repos = "http://cran.us.r-project.org")
```

```{r}
#| output: false
#| echo: false
#| message: false

lapply(packages, require, character.only = TRUE)
```

```{r}
#| output: false
#| echo: false

ds <- read.csv(here("data", "msg.csv"))
```

```{r}
#| echo: false

wordcloud2(data = ds, shape = "cardioid")
```

# sqrt(9) square root
# sqrt(25)
# nchar("snow") number of characters
# nchar("macalester")
# sqrt(nchar("snow"))

# rep(x = 2, times = 5) repeat x for # times
# rep(times = 5, x = 2)
# rep(2, 5) same as line 46
# rep(5, 2) --> x=5, times=2
# seq(from = 2, to = 10, by = 2) sequence numbers from 2 to 10 by 2
# seq(2, 10, 2) same as line 50
# seq(from = 2, to = 10, length = 3) sequence 3 numbers from 2 to 10
# seq(2, 10, 3) sequence numbers from 2 to 10 by 3
# rep(seq(3,12,3),2) combine 2 functions

degrees_c <- -13
degrees_c

degrees_c * (9/5) + 32
degrees_f <- degrees_c * (9/5) + 32
degrees_f

print(degrees_tomorrow) 
#degrees_tomorrow doesn't exist


