---
title: "Summary Sheet"
format: html
---

## Basics of dataset
### import data
survey <- read.csv("URL")


### the dimension of the data frame (number of columns and number of rows)
dim(survey)

### the number of rows of the data frame
nrow(survey)

### the first 6 rows of the data frame (by default)
head(survey)

### the first 3 rows of the data frame
head(survey, 3)

### the last 6 rows of the data frame (by default)
tail(survey)

### the names of the rows of the data frame
names(survey)

### Obtain the overall class of the survey object
class(survey)

### the internal structure of the data frame
str(survey)

## Basics of viz
### general codes for viz:
ggplot(___, aes(x = ___)) + 
  geom___(color = "___", fill = "___") + 
  labs(x = "___", y = "___")
  
### Why viz:
2 types of variables:
 - **response variable**
 - **predictors**
 
exploring relationships between variables:
  - relationship trends: direction & form
  - relationship strength: degree of variability from the trend


## Bar Chart
```{r}
#basic
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
 # geom_bar(color = "___", fill = "___") + [color = color of the outline of bars; fill = color of the fill of bars]
 # labs(title = "___", x = "___", y = "___") +
 # theme_minimal() [optional]


```


  
## Histogram
```{r}
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
 # geom_histogram(color = "___", fill = "___",binwidth = number) + [color = color of the outline of bars; fill = color of the fill of bars; usually binwidth = 30, 200 is also good]
 # labs(title = "___", x = "___", y = "___") +
 # theme_minimal() [optional]
```

## Density Plot: quantitative vs cateogorical
```{r}
#ggplot(dataset, aes(x = VariableForX, y=VariableForY, fill = ExtraVariable)) + 
 # geom_density(color = "___", fill = "___", alpha = 0.5) + [color = color of the outline; fill = color of the fill; alpha = adds transparecy:the closer to 0, the more transparent]
 # scale_fill_manual(values = c("color1", "color2", "color3"))+
 # facet_wrap(~ExtraVariable)
 # labs(title = "___", x = "___", y = "___") +
 # theme_minimal() [optional]
```
  
## Scatter Plot: 2 quantitative var
```{r}
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
#  geom_point(shape = number,color = "__") + [shape = the shape of the points(this is optional, usually the point is in circle, but when shape = 3, the point is in plus sign); color = the color of the points ]
#  geom_smooth(method = "lm") + [add a trend line; method = "lm" --> linear line]
 # labs(title = "___", x = "___", y = "___") +
 # theme_minimal() [optional]

#or
  
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
 # geom_text(aes(label = Variable)) 
```

## Violin & Box Plots: quantitative vs ca
```{r}
#Violin plot:
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
 # geom_violin()

#Box plot:
#ggplot(dataset, aes(x = VariableForX, y=VariableForY)) + 
 # geom_boxplot()
```

## General ggplot2-cheatsheet

```{r}
library(pdftools)
files <- list.files(pattern = "https://github.com/ujjwalkarn/DataScienceR/blob/master/R%20cheat%20sheets/ggplot2-cheatsheet.pdf")
```


## data wrangling-cheatsheet
```{r}
files <- list.files(pattern = "https://github.com/ujjwalkarn/DataScienceR/blob/master/R%20cheat%20sheets/data-wrangling-cheatsheet.pdf")
```

